---
title: "Frequentis Metric Plots"
author: "Isaac Goldstein"
date: '2022-06-16'
output: html_document
---
```{r}
library(tidyverse)
library(rstan)
library(tidybayes)
library(patchwork)
library(EpiEstim)
library(epidemia)
library(rstanarm)
library(lubridate)
library(coda)
options(mc.cores = parallel::detectCores())
rstan_options(auto_write = TRUE)

source(here::here("R", "rt_utility_functions2.R"))

cbPallette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

```

Data generated in:
R/simulation_studies/simulation_scripts/stemr_S1_sims.R
R/simulation_studies/simulation_scripts/stemr_S2_sims.R
R/simulation_studies/simulation_scripts/stemr_S3_sims.R

Data analyzed in:
R/simulation_studies/analysis_scripts/rt_estim_gamma
R/simulation_studies/analysis_scripts/rt_estim_normal
R/simulation_studies/analysis_scripts/epiestim

Results summarised in:
R/simulation_studies/analysis_scripts/rtmetric_list.R

Note that the results were originally run with different notation
"DT" = "S3", "LT" = "S2", "ET" = "S1"
"gamma" = "estimgamma", "epidemia" = "estimnormal"

Primary metric plot
```{r}
final_list <- read_rds(here::here("R", 
                                  "simulation_studies", 
                                  "simulation_results", 
                                  "final_list.rds"))

summary <- map(final_list, ~.x %>%
                      group_by(model, setting))  %>%
          bind_rows(.id = "sim")


# we can at least make the figure

graph_summary <- summary %>%
                 filter(setting != "DT_autokappa" & setting != "DT_wronggen" &
                        setting != "DT_lowtestrho") %>%
                 dplyr::select(model, 
                               setting, 
                               mean_dev, 
                               MCIW, 
                               mean_env, 
                               MASV) %>%
                 pivot_longer(all_of(c("mean_dev", 
                                        "MCIW",
                                        "mean_env",
                                       "MASV")), names_to = "metric")

graph_summary$metric <- as.factor(graph_summary$metric)
level_list <- c("mean_env", "MCIW", "mean_dev", "MASV")



label_list <- c("Envelope", "MCIW", "Deviation", "MASV")
graph_summary$metric <- factor(graph_summary$metric, levels=level_list, labels=label_list)


graph_summary$setting[graph_summary$setting == "ET"] <- "Scenario 1"
graph_summary$setting[graph_summary$setting == "LT"] <- "Scenario 2"
graph_summary$setting[graph_summary$setting == "DT"] <- "Scenario 3"
level_list <- c("Scenario 1", "Scenario 2" , "Scenario 3")

graph_summary$setting <- as.factor(graph_summary$setting)
graph_summary$setting <- factor(graph_summary$setting, levels = level_list)


graph_summary$model <- as.factor(graph_summary$model)


level_list <- c("EpiEstim", "epidemia", "gamma")

label_list <- c("EpiEstim", "Rt-estim-normal", "Rt-estim-gamma")



graph_summary$model <- factor(graph_summary$model, levels = level_list, labels = label_list)


graph_summary <- graph_summary %>%
                 mutate(model_scenario = paste(model, setting, sep = "_"))

level_list <- c("EpiEstim_Scenario 1", 
                "EpiEstim_Scenario 2", 
                "EpiEstim_Scenario 3",
                "Rt-estim-normal_Scenario 1",
                "Rt-estim-normal_Scenario 2",
                "Rt-estim-normal_Scenario 3", 
                "Rt-estim-gamma_Scenario 1",
                "Rt-estim-gamma_Scenario 2",
                "Rt-estim-gamma_Scenario 3")

label_list <- c("EE S1", 
                "EE S2", 
                "EE S3", 
                "EN S1", 
                "EN S2", 
                "EN S3", 
                "EG S1", 
                "EG S2", 
                "EG S3")

graph_summary$model_scenario <- factor(graph_summary$model_scenario, levels = level_list, labels = label_list)

# redoing this with separate bar plots so we can add in dotted lin --------

cov_plot <- graph_summary %>%
            filter(metric == "Envelope") %>%
            ggplot(aes(x = model_scenario, y = value, shape = setting)) +
            geom_boxplot() +
            geom_hline(yintercept=0.95, linetype="dashed") +
            theme_bw() +
            theme(legend.position = "none",
                  axis.text.x = element_blank(),
                  text = element_text(size = 14)) +
            xlab("") +
            ylab("Envelope") +
            ggtitle("Envelope") +
            scale_shape_manual(values = c(0, 1, 2)) 
cov_plot


MCIW_plot <- graph_summary %>% 
  rename("Setting" = "setting") %>%
  filter(metric == "MCIW") %>%
            ggplot(aes(x = model_scenario, y = value, shape = Setting)) +
            geom_boxplot() +
  theme_bw() +
  theme(axis.text.x =element_blank(),
        text = element_text(size = 14),
        legend.position = "none") +
  xlab("") +
  ylab("MCIW") +
  ggtitle("MCIW") +
scale_shape_manual(values = c(0, 1, 2)) 

MCIW_plot



dev_plot <- graph_summary %>%
  filter(metric == "Deviation") %>%
            ggplot(aes(x = model_scenario, y = value, shape = setting)) +
            geom_boxplot() +
  geom_hline(yintercept=0, linetype="dashed") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x =element_text(angle = 10),
        text = element_text(size = 14)) +
  xlab("Method") +
  ylab("Deviation") +
  ggtitle("Absolute Deviation") +
  scale_shape_manual(values = c(0, 1, 2)) 

dev_plot

MASV_plot <- graph_summary %>%
  filter(metric == "MASV") %>%
  rename("Setting" = "setting") %>%
            ggplot(aes(x = model_scenario, y = value, shape = Setting)) +
            geom_boxplot() +
  geom_hline(yintercept = 0.12, linetype = "dashed") +
  theme_bw() +
  theme(legend.position = "none", 
        legend.background = element_rect(fill="transparent"),
        legend.box = "horizontal",
        axis.text.x = element_text(angle = 10), 
        text= element_text(size = 14)) +
  xlab("Method") +
  ylab("MASV") +
  ggtitle("MASV") +
  scale_shape_manual(values = c(0, 1, 2)) 

MASV_plot


primary_metric_plot <- cov_plot + MCIW_plot + dev_plot + MASV_plot
primary_metric_plot
```




# seconday metric plot for the appendices
```{r}
app_summary <- map(final_list, ~.x %>%
                      group_by(model, setting)) %>%
          bind_rows(.id = "sim")
app_graph_summary <- app_summary %>%
                 filter(setting == "DT_autokappa" |
                          setting == "DT_wronggen" |
                          setting == "DT_lowtestrho" |
                          (model == "gamma" & setting == "DT")) %>%
                 dplyr::select(model, 
                               setting, 
                               mean_dev, 
                               MCIW, 
                               mean_env, 
                               MASV) %>%
                 pivot_longer(all_of(c("mean_dev", 
                                        "MCIW",
                                        "mean_env",
                                       "MASV")), names_to = "metric")

app_graph_summary$metric <- as.factor(app_graph_summary$metric)
level_list <- c("mean_env", "MCIW", "mean_dev", "MASV")



label_list <- c("Envelope", "MCIW", "Deviation", "MASV")
app_graph_summary$metric <- factor(app_graph_summary$metric, levels=level_list, labels=label_list)


app_graph_summary$setting[app_graph_summary$setting == "DT"] <- "Default"
app_graph_summary$setting[app_graph_summary$setting == "DT_autokappa"] <- "Kappa"
app_graph_summary$setting[app_graph_summary$setting == "DT_wronggen"] <- "Wrong Gen"
app_graph_summary$setting[app_graph_summary$setting == "DT_lowtestrho"] <- "Alt Rho"
level_list <- c("Default", "Kappa" , "Wrong Gen", "Alt Rho")

app_graph_summary$setting <- as.factor(app_graph_summary$setting)
app_graph_summary$setting <- factor(app_graph_summary$setting, levels = level_list)


app_graph_summary$model <- as.factor(app_graph_summary$model)


level_list <- c("EpiEstim", "epidemia", "gamma")

label_list <- c("EpiEstim", "Rt-estim-normal", "Rt-estim-gamma")



app_graph_summary$model <- factor(app_graph_summary$model, levels = level_list, labels = label_list)


# redoing this with separate bar plots so we can add in dotted lin --------

app_cov_plot <- app_graph_summary %>%
            filter(metric == "Envelope") %>%
            ggplot(aes(x = setting, y = value)) +
            geom_boxplot() +
            geom_hline(yintercept=0.95, linetype="dashed") +
            theme_bw() +
            theme(legend.position = "none",
                  axis.text.x = element_blank(),
                  text = element_text(size = 14)) +
            xlab("") +
            ylab("Envelope") +
            ggtitle("Envelope") +
            scale_shape_manual(values = c(0, 1, 2)) 
app_cov_plot


app_MCIW_plot <- app_graph_summary %>% 
  rename("Model" = "model") %>%
  filter(metric == "MCIW") %>%
  ggplot(aes(x = setting, y = value)) +
            geom_boxplot() +
  theme_bw() +
  theme(axis.text.x =element_blank(),
        legend.position = c(.7, .8), 
        legend.background = element_rect(fill="transparent"),
        legend.box = "horizontal") +
  xlab("") +
  ylab("MCIW") +
  ggtitle("MCIW") +
scale_shape_manual(values = c(0, 1, 2)) 

app_MCIW_plot



app_dev_plot <- app_graph_summary %>%
  filter(metric == "Deviation") %>%
  ggplot(aes(x = setting, y = value)) +
            geom_boxplot() +
  geom_hline(yintercept=0, linetype="dashed") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x =element_text(angle = 10),
        text = element_text(size = 14)) +
  xlab("Scenario") +
  ylab("Deviation") +
  ggtitle("Absolute Deviation") +
  scale_shape_manual(values = c(0, 1, 2)) 

app_dev_plot

app_MASV_plot <- app_graph_summary %>%
  filter(metric == "MASV") %>%
  rename("Model" = "model") %>%
  ggplot(aes(x = setting, y = value)) +
            geom_boxplot() +
  geom_hline(yintercept = 0.12, linetype = "dashed") +
  theme_bw()  +
  theme(axis.text.x = element_text(angle = 10), 
        text= element_text(size = 14),
        legend.position = "none") +
  xlab("Scenario") +
  ylab("MASV") +
  ggtitle("MASV") +
  scale_shape_manual(values = c(0, 1, 2)) 

app_MASV_plot


app_metric_plot <- app_cov_plot + app_MCIW_plot + app_dev_plot + app_MASV_plot
app_metric_plot


app_metric_plot
```
